%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {CMU Accessibility Lab} % Organization
    {Jan, 2019 - Present} % Date(s)
    {Pittsburgh, PA, USA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed an automatic system for blind people to access image memes on social media.}
        \item {Co-authored paper published at \it{ASSETS '19}.}
        \item {Advised by Prof. Jeffrey Bigham.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {CMU CHIMPS Lab} % Organization
    {Fall, 2018 - Present} % Date(s)
    {Pittsburgh, PA, USA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on effectively summarizing terms \& conditions documents using crowdsourcing and machine learning.}
        \item {Submitted a first-author paper to \it{WWW '20}.}
        \item {Advised by Prof. Jason Hong.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {CMU HCII REU program} % Organization
    {May, 2019 - Aug, 2019} % Date(s)
    {Pittsburgh, PA, USA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigated how voice assistants can handle information seeking tasks for blind people.}
        \item {Advised by Prof. John Zimmerman.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Dell EMC} % Organization
    {May, 2018 - Aug, 2018} % Date(s)
    {Beijing, China} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on machine learning based disk failure prediction using SMART and BMS log data.}
        \item {Filed one US patent and two Chinese patents.}
        \item {Won the Best Paper Award of DEll CCOE Product Symposium 2018}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
